%==============================================================================
% Bachelor Thesis Proposal by Dante De Ruwe
%==============================================================================
% Applied Information Technology 2020-2021 
% Faculty of IT and Digital Transformation @ Ghent University College 
% Based on a LaTeX-template by Jens Buysse and Bert Van Vreckem 

\documentclass{proposal} % official template
\usepackage{proposal} % extra additions

% ----------------------------------------
% Metadata
% ----------------------------------------

% --- Title and Author ---
\PaperTitle{
    Enabling the Distributed Development of Blazor-Based Web Applications Using
    a Microfrontend Architecture
}

\PaperType{Bachelor Thesis Proposal 2020-2021}

\Authors{Dante De Ruwe\textsuperscript{1}} 

\CoPromotor{Dr. Florian Rappl\textsuperscript{2} (Solution Architect at smapiot GmbH)}
\affiliation{
    \textbf{Contact:}
    \textsuperscript{1}\mailto{dantederuwe@gmail.com};
    \textsuperscript{2}\mailto{florian.rappl@smapiot.com}
}

% --- Abstract ---
% Hier schrijf je de samenvatting van je voorstel, als een doorlopende tekst van
% één paragraaf. Wat hier zeker in moet vermeld worden: 
% - Context (Waarom is dit werk belangrijk?)
% - Nood (Waarom moet dit onderzocht worden?)
% - Taak (Wat ga je (ongeveer) doen?);
% - Object (Wat staat in dit document geschreven?)
% - Resultaat (Wat verwacht je van je onderzoek?)
% - Conclusie (Wat verwacht je van van de conclusies?)
% - Perspectief (Wat zegt de toekomst voor dit werk?).

\Abstract{With the WebAssembly \textit{(WASM)} standard a new set of web
    applications have been made possible. Within the .NET ecosystem, the most
    popular solution for generating WebAssembly applications is called Blazor.
    This framework allows building interactive web UIs using C\#
    instead of JavaScript. One challenge in this approach is that there is
    no direct way of enabling distributed development. While component libraries
    can be created independently, knowledge in the main application would be
    required for integration. Using a \textit{microfrontend architecture} this
    relationship could be inversed. This thesis investigates what is needed to
    empower the distributed development of large-scale Blazor-based web
    applications, tackling the individual challenges that go along with this on
    its way. To gain insight into the domain, a theoretical study will be
    conducted in 3 phases. Ultimately, a proof-of-concept solution will be
    created to demonstrate the use of a microfrontend architecture in a Blazor
    environment with an almost exclusive .NET-approach. The prediction is that
    this should be feasible, but well-thought-out compromises will have to be
    made regarding the limitations of the current state of the Blazor framework
    and WebAssembly standard. As the adoption of the Blazor framework and the
    microfrontend architecture pattern will mature, this thesis could be a
    valuable resource for .NET-focussed development teams creating large-scale
    full-stack web applications. }

% --- Domain and Key Words ---
\Keywords{
    Web Development
    -- Software Architecture 
    -- Distributed Development
    -- Microfrontends
    -- Blazor
    -- WebAssembly
    -- .NET
    -- C\#
} 

% ----------------------------------------
% Document
% ----------------------------------------

\begin{document}

\flushbottom            % Makes all text pages the same height
\maketitle              % Print the title and abstract box
\tableofcontents        % Print the contents section
\thispagestyle{empty}   % Removes page numbering from the first page


% --- Contents ---
\input{proposal-content}

% --- References ---
\phantomsection
\printbibliography[heading=bibintoc]

\end{document}