% ----------------------------------------
% Inleiding 
% ----------------------------------------

\section{Introduction}
\label{sec:introduction}

The development of applications for the web has seen some dramatic shifts over
the years. Apart from new technologies, protocols and standards, the way web
applications are structured has undergone some evolutions as well. ``Software
architecture'' not only outlines the pure structure of the application, but also
defines the responsibility of all the pieces of the application, and how these
pieces ought to interact with each other \autocite{Fedorov_etal_1998}.

In the ``early days'' of web development, nearly all applications had a
\textit{monolithic} architecture: a single-tier architecture, where the user
interface (UI), business logic and data storage are all managed in a single
all-in-one solution. Now, developer teams have mostly adopted split-stack
development, where the UI is handled in the so-called ``front end'' and the
business and data logic are dealt with by a ``back end'' system. This reduced
coupling enabled specialized teams to develop each aspect individually,
independently and therefore simultaneously \autocite{Dunkley_2016}. For the same
reasons, \textit{microservices} started making an appearance when developers
realized that having a single back-end service could also be considered a
monolithic approach \autocite{Fowler_Microservices_2014}.

In 2016 the ThoughtWorks Technology Radar \autocite{ThoughtWorks_2020} coined
the term ``\textit{Micro Frontends}'' to describe the split of the front-end
monolith into independently deployable and maintainable pieces. This is
especially beneficial for large-scale projects, where the division of developers
in autonomous teams is crucial. However, enabling distributed development of
these micro frontends is not a trivial undertaking, and naturally has its
challenges.

This thesis aims to be an application of this micro frontends pattern, to enable
distributed development of large scale web applications. More specifically, this
thesis will focus on the Blazor\hreffootnote{https://blazor.net} web framework
that uses WebAssembly\hreffootnote{https://webassembly.org/} to execute C\# code
in the browser.

\begin{minipage}{\linewidth} %to keep content together
     The research questions that will be addressed:
    \begin{itemize}
        \item[$RQ_1$] What is needed to be able to independently develop and
        deploy micro frontends using Blazor WebAssembly?
        \item[$RQ_2$] How to render Blazor-based micro frontends with the proper
        isolation, performance and with progressive enhancement in mind?
        \item[$RQ_3$] What are the challenges that need to be overcome, and how
        would one do so? 
        \item[$RQ_4$] How can development teams benefit from the transformation
        of their Blazor monolith into a micro frontend solution?
    \end{itemize}
\end{minipage}

\blankline
Additionally, an objective of this thesis is to generate an open-source
proof-of-concept Blazor web application that implements the micro frontend
architecture pattern.



% ---------------------------------------- 
% State-of-the-art 
% ----------------------------------------

\section{State-of-the-art}
\label{sec:state-of-the-art}

\subsection{Distributed Development}
As software projects grow larger and larger in size, naturally more developers
are needed to maintain them. But the efficiency of teams does not scale
linearly. This is a wisdom that dates back to the very early days of software
development, as proven by the still applicable quote by \textcite{Brooks_1975}:
``adding manpower to a late software project makes it later''.\\
A solution to this is obviously to subdivide the project into chunks, managed by
specialized teams. A company could even let these teams operate from a different
geographical location. This is called ``distributed development''. While there
are major benefits; this significantly increases the need for extensive
coordination and communication between the teams, as well as a good company
structure and strategy. Making this possible all starts with the choice of a
good common architecture that is scalable and supports distributed development
\autocite{Yuhong_2008}. 

\subsection{Why Micro Frontends?}
As outlined in the introduction to this proposal, there is an already widespread
practice of splitting up projects ``horizontally'' per layer or technology. It
makes sure that experts can co-operate together as one team and ensure a high
technical standard within the boundaries of their respective areas of expertise.

But what if a company wants to put its focus on user experience, innovation and
features, instead of purely on creating the most technically perfect solution?
This is where multidisciplinary or cross-functional ``feature teams'' can come
in. These are grouped around a specific business case or customer need. This
``vertical slicing'' has major benefits: it enables teams to be completely
independent and have end-to-end responsibility for the features they develop.
This aids in accelerating development speed, cutting down on inter-team
communication and enabling developers to feel a greater sense of involvement in
the project or product \autocite{LarmanVodde_2008}.

The ``micro frontends'' architecture gives developers the necessary tools to be
able to organize themselves into autonomous ``feature teams'', where each team
has a company mission they specialize in. \autocite{Geers_2020}

\subsection{Composing and Integrating Micro Frontends}
Implementing the micro frontend architecture pattern can be done in various
ways. This proposal will not mention all of them, nor will it provide a detailed
look at any of these techniques. However, below some common methodologies are
outlined. \autocite{Geers_2020} \autocite{Peltonen_etal_2020}
\autocite{Pavlenko_etal_2020}

\begin{itemize}
    \item Page transitions via hyperlinks
    \item Composition via iframe
    \item Composition via AJAX and Web Components
    \item Server-side rendering
    \item Client-side rendering
    \item Universal rendering
\end{itemize}

This thesis will focus on universal (also known as \textit{isomorphic})
rendering. This is a rendering technique that aims to combine client-side and
server-side rendering practices. The main concept is pre-rendering the
application on the server, resulting in a relatively fast initial load, and then
\textit{(re)hydrating} the pre-rendered application on the client side to make
it fully client-side interactive. This enables progressive enhancement.
\autocite{MillerOsmani_2019}

\subsection{Blazor WebAssembly}
According to \textcite{Rappl_MunichNETMeetup_2020}, an easy and effective way to
make distributed development possible in a Blazor WebAssembly project, is simply
to use separately distributed component libraries. In Blazor -- and in the .NET
ecosystem in general -- NuGet\hreffootnote{https://www.nuget.org/} is the
standardized way of library distribution. One could create one overarching web
app which imports and incorporates these NuGet packages. This is often called
the \textit{app shell} \autocite{Geers_2020}. While this implementation pattern
makes development relatively straight-forward, it has its downsides. Because the
integration happens at build-time; any change requires full recompilation of the
entire application. Also, upon startup, all libraries have to be loaded, which
makes this approach sub-optimal regarding scalability. This integration method
re-introduces coupling, and is generally discouraged \autocite{Jackson_2019}.

Integrating Blazor components in a JavaScript based app shell is another option.
While this has been done succesfully\footnote{See an example here:
\hrefself{https://github.com/lauchacarro/MicroFrontend-Blazor-React}}, this is
not within the scope of this thesis, as the focus is on an almost exclusive .NET
approach.

The desired solution, in contrast to the aforementioned approaches, uses
\textit{``C\#.NET all the way''} if possible, and has run-time integration with
dynamic (lazy) loading capabilities. In this, the challenges may come because of
the Blazor Intermediate Language (IL) trimming, which removes unused code and
libraries in the output assemblies \autocite{Latham_2020}. Luckily, .NET 5
introduces lazy loading capabilities for Blazor out of the box
\hreffootnote{https://docs.microsoft.com/en-us/aspnet/core/blazor/webassembly-lazy-load-assemblies},
\autocite{Kdouh_2020} \autocite{Rappl_dotNETConf_2020}, yet it is unclear if
this is the cure-all solution.

It should also be repeated, that progressive enhancement is desired. The
combination of these requirements will be achieved by using universal rendering,
but with the focus on the server-side.




% ---------------------------------------- 
% Methodology 
% ----------------------------------------

\section{Methodology}
\label{sec:methodology}

\subsection{Theoretical study}
To be able to answer the research questions, a theoretical study will be
conducted in 3 phases:
\begin{itemize}
    \item Phase 1: Providing an overview of the micro frontend architecture and
    the key differences with a monolithic architecture.
    \item Phase 2: Exploring implementation patterns, challenges and best
    practices of the micro frontends pattern in a Blazor WebAssembly project.
    \item Phase 3: Investigating the benefits and drawbacks of using the micro
    frontends architecture with the goal of enabling distributed development in
    a company context.
\end{itemize}

\subsection{Proof-of-concept}
With the gained insight of the literature and the theoretical study, a
proof-of-concept solution around a realistic business case will be created to
demonstrate the practical application of the micro frontends architecture
pattern in a Blazor WebAssembly project. Ideally, this PoC will be made
open-source.



% ---------------------------------------- 
% Expected results 
% ----------------------------------------

\section{Expected Results}
\label{sec:expected-results}

The expected results of the theoretical study are relatively straightforward. In
\textit{phase 1}, further insight will be gained into the micro frontend
architecture pattern. \textit{Phase 2} is predicted to provide valuable
knowledge for the eventual proof of concept solution. In particular, the
challenges that will undoubtedly come up in this phase, will be important
considerations for the proof-of-concept solution. Some expected challenges
include debugging, assembly sharing, dynamic loading in combination with IL
trimming ($\approx$ tree shaking), etc... With the results of research
\textit{phase 3}, insight can be gained into the cost-benefit balance of the
micro frontends approach; and indicate when and for whom it is appropriate. 

The proof-of-concept should be feasible to create, but well- thought-out
compromises will have to be made regarding the limitations of the current state
of the Blazor framework and WebAssembly standard.



% ---------------------------------------- 
% Expected conclusions 
% ----------------------------------------

\section{Expected Conclusions}
\label{sec:expected-conclusions}

The distributed development of Blazor-based web applications, using the micro
frontends pattern, with an almost exclusive .NET approach should be possible.
Because of the complexity of integration, this is only beneficial to large
teams, or teams that expect scaling. Judging by the limited maturity of Blazor
and the application of the micro frontends pattern within this tech stack, this
thesis could provide one of the first business cases within this specific area.