% ----------------------------------------
% Preface
% ----------------------------------------

\chapter*{Preface}
\label{ch:preface}

This bachelor's thesis was written as a part of the final steps of obtaining my
professional bachelor's degree in \textit{Applied Information Technology} at
Ghent University of Applied Sciences and Arts
(HoGent). During the past years, I discovered
my passion for software architecture and development, mainly focussed on
.NET-related technologies.

My introduction into the wonderful world of \glsplural{microfrontend} started
when applying for an international internship in the summer of 2020. I came into
contact with the company ``smapiot'' and one of their solution architects,
Florian Rappl. He introduced the concept of the \gls{mfa} to me, mentored me
through my internship entirely focussed around that architecture, and provided
me with the inspiration for this thesis.\\
\Glsplural{microfrontend} were right outside of my comfort zone. I was most
familiar with \gls{backend} development and architecture, and had almost no idea
there was a need for distributed architectures in the \gls{frontend} space to
begin with. The international internship really pulled me deeper into the topic,
and provided me with hands-on experience.

I want to sincerely thank Florian for his mentorship during the internship, for
being the co-promotor of this thesis, and for providing me with useful guidance
and sources. 

Many thanks also to Benjamin Vertonghen for being the promotor of
this thesis. He provided me with useful feedback and was available for my
questions even during the vacation period.

Next, I want to take this opportunity to thank my family -- with in particular
my mother, father, sister and stepfather -- for mentally, practically and
financially supporting me throughout my entire study career. Without them I
would not be where I am today.

Finally, a big thank you to my girlfriend, for her continued love and support,
even throughout the COVID-19 pandemic, the 3-month-long internship abroad, and
the process of writing this thesis.